---
title: "BioVenn Tutorial"
output: rmarkdown::html_vignette
description: >
  Start here if this is your first time using BioVenn. You'll learn how to
  create area-proportional Venn diagrams from two or three circles.
vignette: >
  %\VignetteIndexEntry{BioVenn Tutorial}
  %\VignetteEngine{knitr::rmarkdown}
  \usepackage[utf8]{inputenc}
---

```{r, echo = FALSE, message = FALSE}
library("BioVenn")
```

## Example diagram 1: 3-circle diagram with absolute numbers

Create three lists of Affymetrix IDs.

```{r}
list_x <- c("1007_s_at","1053_at","117_at","121_at","1255_g_at","1294_at")
list_y <- c("1255_g_at","1294_at","1316_at","1320_at","1405_i_at")
list_z <- c("1007_s_at","1405_i_at","1255_g_at","1431_at","1438_at","1487_at","1494_f_at")
```

Create the BioVenn diagram, using the three lists as input. The subtitle is set to "Example diagram 1", and absolute numbers will be displayed.
The function prints the resulting numbers.

```{r, fig.dim = c(10, 10), out.width="100%"}
biovenn <- draw.venn(list_x, list_y, list_z, subtitle="Example diagram 1", nrtype="abs")
```

The returned object contains the thirteen lists (the sets and their overlaps).

```{r}
biovenn
```

## Example diagram 2: 2-circle diagram with percentages

Create two lists of Ensembl IDs.

```{r}
list_x <- NULL
list_y <- c("ENSG000000001","ENSG000000002","ENSG000000003","ENSG000000004","ENSG000000005","ENSG000000006")
list_z <- c("ENSG000000001","ENSG000000004","ENSG000000007","ENSG000000008","ENSG000000009")
```

Create the BioVenn diagram, using the two lists as input. The subtitle is set to "Example diagram 2", and percentages will be displayed.
The function prints the resulting numbers.

```{r, fig.dim = c(10, 10), out.width="100%"}
biovenn <- draw.venn(list_x, list_y, list_z, subtitle="Example diagram 2", nrtype="pct")
```

The returned object contains the thirteen lists (the sets and their overlaps).

```{r}
biovenn
```

## Example diagram 3: 3-circle diagram with ID mapping

Create three lists of Affymetrix IDs.

```{r}
list_x <- c("1007_s_at","1053_at","117_at","121_at","1255_g_at","1294_at")
list_y <- c("1255_g_at","1294_at","1316_at","1320_at","1405_i_at")
list_z <- c("1007_s_at","1405_i_at","1255_g_at","1431_at","1438_at","1487_at","1494_f_at")
```

Create the BioVenn diagram, using the three lists as input. The subtitle is set to "Example diagram 3", and absolute numbers will be displayed.
Affymetrix IDs will be mapped to Ensembl IDs. The function prints the resulting numbers.

```{r, fig.dim = c(10, 10), out.width="100%"}
biovenn <- draw.venn(list_x, list_y, list_z, subtitle="Example diagram 3", nrtype="abs", map2ens=TRUE)
```

The returned object contains the thirteen lists (the sets and their overlaps).

```{r}
biovenn
```

## Example diagram 4: 3-circle diagram with altered colours

Create three lists of Affymetrix IDs.

```{r}
list_x <- c("1007_s_at","1053_at","117_at","121_at","1255_g_at","1294_at")
list_y <- c("1255_g_at","1294_at","1316_at","1320_at","1405_i_at")
list_z <- c("1007_s_at","1405_i_at","1255_g_at","1431_at","1438_at","1487_at","1494_f_at")
```

Create the BioVenn diagram, using the three lists as input. The subtitle is set to "Example diagram 4", and absolute numbers will be displayed.
The background colour will be black, with different circle colours and white text. The function prints the resulting numbers.

```{r, fig.dim = c(10, 10), out.width="100%"}
biovenn <- draw.venn(list_x, list_y, list_z, t_c="#FFFFFF", subtitle="Example diagram 4", st_c="#FFFFFF", xt_c="#FFFFFF", yt_c="#FFFFFF", zt_c="#FFFFFF", nrtype="abs", nr_c="#FFFFFF", x_c="#FFFF00", y_c="#FF00FF", z_c="#00FFFF", bg_c="#000000")
```

The returned object contains the thirteen lists (the sets and their overlaps).

```{r}
biovenn
```
